Language Use in a Multilingual Tweet Corpus

### 2018-07-19 paper.tex
Final tweaks

%However, the question of whether the collection is any good remains open. It would be easy to test its extrinsic properties, for example, whether it leads to improvements in a language identification system when used as training data. But does not reveal its intrinsic properties. Nevertheless, we believe the presented dataset is useful across different studies.

>>>>

However, the question of whether the collection is any good remains open. It would be easy to test its extrinsic properties, for example, whether it leads to improvements in a language identification system when used as training data. But does not reveal its intrinsic properties. Nevertheless, we believe the presented dataset is useful across different studies.
